### 2015-05-27 writing/SNLI paper/transfer.tex
Pre workshopping cleanup.

We first evaluate on SICK (\citealt{marelli2014sick}), the smaller entailment corpus SNLI was modeled on, training on the standard 4.5k training sentence pairs. We then evaluate on SUBJ (\citealt{pang2004sentimental}), a two-way sentence classification task, using 5-fold cross-validation over the 10k sentences. We next evaluate on the SST (\citealt{socher2013acl1}), a five-way sentiment classification task with labels for both phrases and sentences. We train on both types of label within the 8.5k sentence training set and test on only the sentence-level labels in the test set. We finally evaluate on PragBank, an 800 example 6-way sentence classification task focused on veridicality. \todo{Cite} ....

@@

\todo{Do we still want to re-initialize LRs?}
\todo{Do we want to use all four target tasks?}

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c}
\hline
\textbf{Corpus} & \multicolumn{2}{c}{\b{Train Acc.}} &\multicolumn{3}{c}{ \b{Test Acc.}} \\
 & \t{cold start} & \t{transfer} & \t{cold start} & \t{transfer} & \t{SotA} \\
\hline
\t{SICK}            & \t{98} & \t{95} & \t{63?} & \t{80.0?} & \t{84.5} \\
\t{SUBJ}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?}& \t{??.?} \\
\t{SST}          & \t{??.?} & \t{??.?} & \t{43?} & \t{43?} & \t{50.6}\\
\t{PragBank}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?}& \t{??.?} \\
\hline
\end{tabular}
\end{center}

@@

The final column shows the state of the art results from \cite{lai2014illinois}, TODO, \cite{tai2015improved}, TODO, respectively.
\todo{Does Tai have the SotA on SST?}

@@

\todo{something about the state of the art on the other tasks.}

>>>>

We first evaluate on SICK (\citealt{marelli2014sick}), the smaller entailment corpus SNLI was modeled on, training on the standard 4.5k training sentence pairs. We then evaluate on SUBJ (\citealt{pang2004sentimental}), a two-way sentence classification task, using 5-fold cross-validation over the 10k sentences. We next evaluate on the SST (\citealt{socher2013acl1}), a five-way sentiment classification task with labels for both phrases and sentences. We train on both types of label within the 8.5k sentence training set and test on only the sentence-level labels in the test set. We finally evaluate on PragBank, an 800 example 6-way sentence classification task focused on veridicality. \todo{Cite} ....
\noindent\todo{Pick best 2-3 tasks.}

@@

\noindent\todo{Do we still want to re-initialize LRs?}

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c}
\hline
\textbf{Corpus} & \multicolumn{2}{c}{\b{Train Acc.}} &\multicolumn{3}{c}{ \b{Test Acc.}} \\
 & \t{cold start} & \t{transfer} & \t{cold start} & \t{transfer} & \t{SotA} \\
\hline
\t{SICK}            & \t{100} & \t{99} & \t{62.9?} & \t{79.8?} & \t{84.5} \\
\t{SUBJ}          & \t{??.?} & \t{??.?} & \t{90?} & \t{91?}& \t{95.5} \\
\t{SST}          & \t{??.?} & \t{??.?} & \t{43?} & \t{42?} & \t{50.6}\\
\t{PragBank}          & \t{??.?} & \t{??.?} & \t{50} & \t{56}& \t{~75} \\
\hline
\end{tabular}
\end{center}

@@

The final column shows the state of the art results from \cite{lai2014illinois}, \cite{zhao2015self}, \cite{tai2015improved}, TODO, respectively.
\noindent\todo{Does Tai have the SotA on SST?}

@@

\noindent\todo{something about SotA on the other tasks.}
